---
title: "Presentation"
author: "AGDamsbo"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE)
```

```{r}
library(microbenchmark)
library(daDoctoR)
library(stRoke)
```


## R Markdown

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## New cpr_sex()  -to-  cpr_female()

```{r}
print(daDoctoR::cpr_sex)
```

## (continued)

```{r}
print(stRoke::cpr_female)
```


## Testing vectorised version of cpr_female()

```{r echo = TRUE}
fsd<-c("231045-0637", "010115-4000",
       "0101896000","010189-3000",
       "300450-1030","010150-4021")
microbenchmark::microbenchmark(
  stRoke::cpr_female(fsd),
  daDoctoR::cpr_sex(fsd))
```

## Testing vectorised version of cpr_dob()

```{r echo = TRUE}
microbenchmark::microbenchmark(
  stRoke::cpr_dob(fsd),
  daDoctoR::dob_extract_cpr(fsd))
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

